
\documentclass[12pt]{article}

\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}

\pagestyle{empty}
\geometry{margin=0.5in}
\setlength\parindent{9pt}
\setlist{nosep}
\renewcommand\labelitemi{--}

\definecolor{highlight}{RGB}{0, 0, 112}

\newcommand{\name}[1]{\begin{center}\section*{\huge \color{highlight} #1}\end{center}}
\newcommand{\topinfo}[1]{\begin{center}\vspace{-0.2cm}#1\vspace{-0.2cm}\end{center}}
\newcommand{\resumesection}[1]{\vspace{-0.3cm}\section*{\color{highlight}#1}\vspace{-0.3cm}\hrule\vspace{0.3cm}}

\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\name{Peter Zhang}
\topinfo{petejzh@gmail.com  \textbullet\ 240-994-2204}
\topinfo{peterzhang.me \textbullet\ LinkedIn: petezh \textbullet\ GitHub: petezh}


\resumesection{Education}

\textbf{Montgomery Blair High School} Silver Spring, MD; GPA: 3.96 \hfill Class of 2020

\begin{itemize}
	\item Coursework: Analysis of Algorithms, Artificial Intelligence, Algorithms and Data Structures, Graphics, Statistics, Analysis I and II, Complex Analysis, Discrete Math, Logic, Computational Methods
	\item Scores: ACT - 36; SAT - 1570
\end{itemize}


\resumesection{Skills}


\textbf{Programming Languages}
\begin{itemize} 
	\item Java, Python, C\texttt{+}\texttt{+}, HTML/CSS, Javascript/ReactJS, PHP/SQL, R, MATLAB, \LaTeX, Bash.
\end{itemize}\vspace{0.1cm}

\textbf{Applications}
\begin{itemize} 
	\item MS Office, MiniTab, Autodesk Inventor/Blender.
\end{itemize}

\resumesection{Research}

\textbf{Multiple-Instance Learning for Group Testing} \hfill Jul 2019--Present\par
\textit{Georgetown University CS Department; Prof. Bolton}
\begin{itemize}
	\item Applied multiple-instance learning algorithms to group testing.
\end{itemize}\vspace{0.1cm}

\textbf{Root and Rule-Based Natural Language Processing}  \hfill Jun 2019--Present\par
\textit{NIST; Dr. Bhat \& CMU CS Department; Prof. Monarch}
\begin{itemize}
	\item Designed and implemented algorithms for building ontologies and RDFs
	\item Incorporated into NIST's \href{https://randr.nist.gov/mgi/default.aspx}{MGI Data Repository}.
\end{itemize}\vspace{0.1cm}

\textbf{Neural Cryptanalysis for Classical Ciphers} \hfill Apr 2019--Jul 2019\par
\textit{UMD CS Department; Prof. Gasarch}
\begin{itemize}
	\item Introduced novel applications of ANNs to perform cryptanalysis on classical ciphers.
\end{itemize}\vspace{0.1cm}

\textbf{Systems Modeling of Carrying Capacity} \hfill Apr 2019\par
\textit{Independent Research}
\begin{itemize}
	\item Used modern computational methods to model Earth's human carrying capacity.
	\item Designated Finalist in the International Mathematics Modeling Competition
\end{itemize}


\resumesection{Awards}

American Regional Mathematics League; Division A, 8th Place \hfill May 2019 \par
International Mathematics Modeling Challenge; Finalist \hfill May 2019\par
Ronald Reagan Great Communicators Debate; Mid-Atlantic Champion \hfill April 2019\par
Blue Ocean Entrepreneurship Competition; Semi-finalist \hfill March 2019\par
High School Mathematics Modeling Challenge; Finalist \hfill Feb 2019\par
Hack Pennsylvania; Best in Show \hfill Jan 2019\par
USA Computing Olympiad; Gold Division \hfill Jan 2019\par
Carnegie Mellon Informatics and Mathematics Competition; Computer Science Finalist \hfill Jan 2018\par


\end{document}
