\documentclass[11pt]{article}

\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{bbding}

\pagestyle{empty}
\geometry{margin=0.5in}
\setlength\parindent{9pt}
\setlist{nosep}
\renewcommand\labelitemi{--}

\definecolor{highlight}{RGB}{45, 85, 180}

\newcommand{\name}[1]{\begin{center}\section*{\huge \color{highlight} #1}\vspace{-0.6cm}\end{center}}
\newcommand{\topinfo}[1]{\begin{center}\vspace{-0.2cm}#1\vspace{-0.2cm}\end{center}}
\newcommand{\resumesection}[1]{\vspace{-0.8cm}\section*{\color{highlight}#1}\vspace{-0.3cm}\hrule\vspace{0.2cm}}

\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\name{Peter Zhang}
\topinfo{\faHome \ 15429 Indianola Drive, Derwood, MD 20855, USA}
\topinfo{\href{mailto:petez@berkeley.edu}{\faEnvelope \ petez@berkeley.edu} \ \faPhone \ (240) 994-2204 \ \href{https://peterzhang.info/}{\faBriefcase \ peterzhang.info} \  \href{https://github.com/petezh}{\faGithub \ petezh} \  \href{https://www.linkedin.com/in/pjz/}{\faLinkedinSquare \ pjz}}

\resumesection{Education}

\textbf{University of California, Berkeley\hfill Berkeley, CA} \par
\textit{Computer Science \& Economics (intended) B.A.}; 3.98 GPA \hfill 2020--2023\par
\textbf{Coursework:} Data Structures/Algorithms, Data Science, Artificial Intelligence, Discrete Math, Statistics/Probability\par
\textbf{Activities:} Voyager Consulting, The Daily Californian, Debate Society of Berkeley, Computer Science Mentors, UPE

\resumesection{Experience}

\textbf{Computer Science Mentors \hfill Berkeley, CA} \par
\textit{ Mentor} \hfill Sep 2020--Present \par
\begin{itemize}
	\item As junior mentor, prepared/presented weekly lessons and practice problems for six CS 61A students.
	\item As content mentor, prepared worksheets for 100+ mentors and students; wrote script to track 400+ problems.
	\item As senior content mentor, oversee content creation process and lead initiatives for new, improved problems.
\end{itemize}\vspace{0.1cm}

\textbf{Amazon Web Services \hfill Arlington, VA}\par
\textit{Software Development Engineer Intern} \hfill Jun 2021--Aug 2021
\begin{itemize}
	\item Designed/implemented a lightweight, flexible library/tool no notify 1000s of customers across services in <1min.
	\item Rapidly developed/tested/iterated using Java/Typescript, Python, \& AWS services, exceeding performance goals.
\end{itemize}\par

\textbf{Center for Effective Global Action \hfill Berkeley, CA}\par

\textit{Research Apprentice} \hfill Jan 2021--May 2021
\begin{itemize}
	\item To support Open Policy Analysis, developed an R Shiny/markdown showcase and drafted a set of guidelines.
	\item Working with authors, assessed and improved reproducibility for 5 papers using R, Stata, Python, and \LaTeX.
\end{itemize}\par

\textbf{Foundation for Advanced Education in the Sciences \hfill Bethesda, MD} \par
\textit{Teaching Assistant} \hfill Jan 2021, Mar 2021 \par
\begin{itemize}
	\item Taught two sessions of a 3-week introductory Python course with 15 graduate students at the NIH.
	\item Facilitated Slack discussions, held 10+ 1-on-1 office hours, and graded student assignments.
\end{itemize}\vspace{0.1cm}

\textbf{The Bronx High School of Science \hfill Bronx, NY} \par
\textit{Assistant Debate Coach}  \hfill Aug 2020--May 2021
\begin{itemize}
	\item Led 2 practices/week for 30+ Lincoln-Douglas debaters and drilled 1-on-1, qualifying to the nat. championship. 
	\item Judged and coached at 18 national, multi-day tournaments, providing strategic advice and feedback to competitors.
\end{itemize}\vspace{0.1cm}

\textbf{War Room Debate \hfill Austin, TX} \par
\textit{Debate Instructor}  \hfill Jun 2020 \par
\begin{itemize}
	\item Designed sample cases and recorded demo videos for an advanced Lincoln-Douglas debate curriculum
	\item Led lab of 15 students for two weeks of skills lectures, frequent drills, and practice debates.
\end{itemize}\vspace{0.1cm}

\textbf{Premier Debate America \hfill  Los Angeles, CA} \par
\textit{Product Manager/Writer} \hfill Dec 2018--Present \par
\begin{itemize}
	\item Led bi-monthly publication of 18 briefs with 200+ pages of topic research used by thousands of debaters.
	\item Design and maintain \href{https://www.premierdebate.com/briefs/}{premierdebate.com} using Wordpress and CSS/Javascript with 140,000+ visitors since 2019.
\end{itemize}

\resumesection{Projects}

\textbf{\href{https://github.com/petezh/E-Debate}{Debate Analysis}} \hfill Sep 2020--Feb 2021\par
\begin{itemize}
	\item Scraped 200k+ outcomes from debate tournaments and 5k+ online debate cases with a Bsoup/Selenium crawler.
	\item Published articles detailing the \href{https://www.vbriefly.com/2020/12/31/five-trends-among-e-debate-competitors-by-peter-zhang/}{impact of transitioning to online debate} and \href{https://www.vbriefly.com/2021/01/22/disclosure-in-numbers-by-peter-zhang/}{rates of public case disclosure}.
\end{itemize}\vspace{0.1cm} \par

\resumesection{Skills}

\textbf{Languages:} Python, Java/Typescript, R, SQL/MySQL, HTML/CSS/JavaScript, MATLAB, \LaTeX, Stata \par
\textbf{Tools:} Git/Terminal, Azure/AWS, VSCode/IntelliJ/Android Studio, WordPress, Electron

\resumesection{Awards}

UC Berkeley Leadership Award; Recipient \hfill Jul 2020/Aug 2021 \par
Venture Capital Investment Competition; National Finalist \hfill Apr 2021\par
National Speech and Debate Tournament; 6th Place \hfill Jun 2020 \par
USA Computing Olympiad; Platinum Division \hfill Apr 2020 \par

\end{document}
